Functory: A Distributed Computing Library \\ for Objective Caml \thanks{This research was partly supported by the French national project U3CAT (\emph{Unification of Critical C Code Analysis Techniques}, ANR-08-SEGI-021).}

### 2011-02-25 doc/tfp-2011/main.tex
*** empty log message ***

\documentclass[a4paper,12pt]{article}

@@

\usepackage{fullpage,comment,amsmath,graphicx,color,url}

@@

\title{Functory: Distributed Computing \\ for the Common Man\thanks{This
    research was partly supported by the French national project U3CAT
    (\emph{Unification of Critical C Code Analysis Techniques},
    ANR-08-SEGI-021).}} 
%\subtitle{Subtitle Text, if any}

\author{Jean-Christophe Filli\^{a}tre \quad K. Kalyanasundaram \\
  CNRS, LRI, Univ Paris-Sud 11, Orsay F-91405\\
  INRIA Saclay - \^{I}le-de-France, ProVal, Orsay, F-91893 \\
   \url{filliatr@lri.fr, kalyan.krishnamani@inria.fr}}

@@

@@

\section{API}\label{sec:API}
In this section, we describe the
generic API which we shall extend with several specialized
functions in the next section. The main function in our API follows the idea
sketched in the introduction. It has the following signature:
\begin{ocaml}
  val compute : 
    worker:('a -> 'b) -> 
    master:('a * 'c -> 'b -> ('a * 'c) list) -> 
    ('a * 'c) list -> unit
\end{ocaml}
Tasks are pairs, of type \of{'a * 'c}, where the first component is
passed to the worker and the second component is local to the master.
The \ocaml{worker} function should be pure\footnote{We mean
  \emph{observationally pure} here but we allow exceptions to be
  raised to signal failures.} 
and is executed in parallel
in all worker processes. The function \ocaml{master}, on the
contrary, can be impure and is only executed in the master process.
The \ocaml{master} function typically stores results 
in some internal data structure.
Additionally, it may produce new tasks, as a list of type 
\of{('a * 'c) list}, which are then appended to the current set of
pending tasks.
The next section will describe the usage of this generic interface to
perform the traditional map and fold operations.

@@

\section{Derived API}\label{sec:derived}

@@

@@

\section{Illustrative Case Studies}\label{sec:studies}

@@

\section{Implementation Details}\label{sec:implem}

\subsection{Multiple Cores}

The \of{Cores} module implements the distributed computing library for
multiple cores on the same machine. 
% As illustrated in Section~\ref{sec:example}, 
It provides a function
\of{set_number_of_cores: int -> unit} to indicate the number of cores
to be used. The number passed to this function may be different from
the actual number of cores in the machine; it is rather the number of
tasks to be performed simultaneously.
% TODO comment more on the number of cores?
% Thus a program using the \of{Cores} module typically begins with 
% \begin{ocaml}
% open Cores
% let () = set_number_of_cores 8
% \end{ocaml}

The scheduling of tasks to the different cores is left to the
operating system, through \of{Unix.fork}. Thus it may be the case that
two tasks are executed on the same core, even if the declared number
of cores is less or equal than the actual number of cores on the machine.
% TODO: comment on user-provided scheduling?

\subsection{Network of Machines}

\subsubsection{Protocol}\label{sec:protocol}

\subsubsection{Network Sub-modules} % TODO: change title

% There is
% actually a single, generic implementation, which is then instantiated
% in three different ways, corresponding to the three scenarios.  The
% generic implementation assumes that only strings are being transmitted
% over the network, as evident from the \of{Assign} and \of{Completed}
% messages in Section~\ref{sec:protocol}. Depending on the
% implementation, these strings could be marshaled closures, marshaled
% values or simply user strings.

\subsubsection{Fault Tolerance}\label{sec:fault}

\section{Experiments}\label{sec:experiments}

>>>>

\documentclass[tfpsymp,pagenumbers]{tfp07symp}

@@

\usepackage{comment,amsmath,graphicx,color,url}

@@

\title{Functory: A Distributed Computing Library \\ for Objective Caml 
\thanks{This
    research was partly supported by the French national project U3CAT
    (\emph{Unification of Critical C Code Analysis Techniques},
    ANR-08-SEGI-021).}}

\author{Jean-Christophe Filli\^{a}tre \and K. Kalyanasundaram}
\authorrunning{J.-C. Filli\^atre \and K. Kalyanasundaram}

\institute{
  CNRS, LRI, Univ Paris-Sud 11, Orsay F-91405\\
  INRIA Saclay - \^{I}le-de-France, ProVal, Orsay, F-91893 \\
   \email{filliatr@lri.fr, kalyan.krishnamani@inria.fr}}

@@

% PLAN
% 1. introduction, including related work
% 2. API
%    2.1 low level, compute, derived APIs
%    2.2 five different implementations
% 3. implementation
%    3.1 marshalling
%    3.2 protocol
%    3.3 fault tolerance
% 4. experiments

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{API}\label{sec:API}

\subsection{compute}

In this section, we describe the
generic API which we shall extend with several specialized
functions in the next section. The main function in our API follows the idea
sketched in the introduction. It has the following signature:
\begin{ocaml}
  val compute : 
    worker:('a -> 'b) -> 
    master:('a * 'c -> 'b -> ('a * 'c) list) -> 
    ('a * 'c) list -> unit
\end{ocaml}
Tasks are pairs, of type \of{'a * 'c}, where the first component is
passed to the worker and the second component is local to the master.
The \ocaml{worker} function should be pure\footnote{We mean
  \emph{observationally pure} here but we allow exceptions to be
  raised to signal failures.} 
and is executed in parallel
in all worker processes. The function \ocaml{master}, on the
contrary, can be impure and is only executed in the master process.
The \ocaml{master} function typically stores results 
in some internal data structure.
Additionally, it may produce new tasks, as a list of type 
\of{('a * 'c) list}, which are then appended to the current set of
pending tasks.
The next section will describe the usage of this generic interface to
perform the traditional map and fold operations.

@@

\subsection{Low-level API}

% TODO

\subsection{Derived API}\label{sec:derived}

@@

\subsection{Deployment Scenarios}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Implementation Details}\label{sec:implem}

\begin{comment}
  \subsection{Multiple Cores}

  The \of{Cores} module implements the distributed computing library
  for multiple cores on the same machine.
  % As illustrated in Section~\ref{sec:example},
  It provides a function \of{set_number_of_cores: int -> unit} to
  indicate the number of cores to be used. The number passed to this
  function may be different from the actual number of cores in the
  machine; it is rather the number of tasks to be performed
  simultaneously.
  % TODO comment more on the number of cores?  Thus a program using
  % the \of{Cores} module typically begins with
  % \begin{ocaml}
  %   open Cores let () = set_number_of_cores 8
  % \end{ocaml}

  The scheduling of tasks to the different cores is left to the
  operating system, through \of{Unix.fork}. Thus it may be the case
  that two tasks are executed on the same core, even if the declared
  number of cores is less or equal than the actual number of cores on
  the machine.
  % TODO: comment on user-provided scheduling?
\end{comment}

\subsection{Marshaling}

  % There is actually a single, generic implementation, which is then
  % instantiated in three different ways, corresponding to the three
  % scenarios.  The generic implementation assumes that only strings
  % are being transmitted over the network, as evident from the
  % \of{Assign} and \of{Completed} messages in
  % Section~\ref{sec:protocol}. Depending on the implementation, these
  % strings could be marshaled closures, marshaled values or simply
  % user strings.

\subsection{Protocol}\label{sec:protocol}

%\subsubsection{Protocol}

\subsection{Fault Tolerance}\label{sec:fault}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Experiments}\label{sec:experiments}

% \section{Illustrative Case Studies}\label{sec:studies}

@@
